---
title: "SimulationCVsBySimulation"
author: "Rebecca Kurtz-Garcia"
date: "5/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

In this document I attend to recreate the fixed-b critical values generated in LLSW and Sun2008Optimal.  The method I am choosing to use is based on a simulation for the Bartlett kernel with $b= 0.02, 0.04, \dots, 0.98, 1$ with significance level $90%, 95%, 97.5%, and 99%$.  I will be 50,000 replicates with normalized partial sums of 1000 iid standard normal random variables to replicate the Brownian motion process.  To do this simulation I will follow the steps outlined in the next section, and essentially do a permutation method to estimate the distribution. For now I focus on the Bartlett kernel and a t-statistic ($m=1$), and create critical value functions in the following form: 

$$cv(b) = a_0 + a_1 + b + a_2 b^2 + a_3 b^3$$

This was the method used by Keifer and Vogelsang (2005), LLSW, and SPJ2008. I will also do the lugsail transformation for this kernel. 

# Bartlett

Procedure to generate 5,000 test statistics, each with a sample size of 1000. The procedure is described below. 

Kernel functions used 

$$\text{Bartlett} = 1 - |x| \text{ for } |x|<1 $$

## Simulation 

The first method here gets the CVs based on a simulation for LLSW for the standard Bartlett Kernel. 

```{r}
#  What bs to use ---------------------------------------------------------
try_b =  seq(0.005, .99, by = 0.005)


# Autocovariance matrices -------------------------------------------------
# h = lag 
R = function(h, the_sim_data){
  big_T = nrow(the_sim_data)
  index = 1:(big_T -h)
  
  # Already centered
  est = lapply(index, function(i){
      est = the_sim_data[i, ]%*%t(the_sim_data[(i+h), ])
  })
  
  # Sum together
  autocov_s = Reduce('+', est)/big_T
    
  # Because of symmetry 
  if(h!=0){
    autocov_s = autocov_s + t(autocov_s)
  }
  
  return(autocov_s)
}



# Bartlett Kernel Estimator -----------------------------------------------
bartlett = function(x){
  if(abs(x)<1){
    k_x = 1-abs(x)
  } else{
    k_x = 0 
  }
  return(k_x)
}


# Lugsail Bartlett Kernel Estimator -----------------------------------------------
lugsail_bartlett = function(x, r, c){
  
  # Actual lugsail 
  y1 = bartlett(x)/(1-c) 
  y2 = 0 
  
  if(abs(x) < 1/r){
    y2 = bartlett(x*r)*c/(1-c) 
  }
  y = y1- y2
  
  
  return(y)
}

# Recommended b using Andrews rule
lugsail_parameters = function(big_T = 200, b = .071, q = 1, method = "Zero"){
  
  if(method == "Over"){
    r = 3
    c = 2/(1+r^q)
    
  } else if(method == "Adaptive"){
    r = 2
    M  = big_T * b
    c_num = (log(big_T) - log(M) + 1)
    c_den = r^q*(log(big_T) - log(M)) + 1
    c = c_num/c_den 
    
  } else {
    # Zero or Manual lugsail
    r = 2
    c = r^(-q)
    
  }
  parameters = list(r = r, c = round(c, 2))
  return(parameters)
}


# Get F-statistic Function -----------------------------------------------
get_F_stats = function(b, sim_data, the_means, all_autocovariances, lugsail_parameters = F){
  M = b*nrow(sim_data)
  W = rep(0, nrow(all_autocovariances))
  if(length(lugsail_parameters) == 1 ){
     weights = sapply(0:(M)/(M+1), bartlett) 
  } else{
    weights = sapply(0:(M)/(M+1), lugsail_bartlett, 
                     r= lugsail_parameters$r, 
                     c = lugsail_parameters$c) 
  }
  
  W[1:length(weights)] = weights
  dim = length(the_means)
  big_T = nrow(sim_data)
  omega = matrix(colSums(W * all_autocovariances)/big_T, dim, dim) 
  m_max = ncol(sim_data)
  F_stat = sapply(1:m_max, function(m){
    omega_inv = solve(omega[1:m, 1:m])
    F_stat = the_means[1:m]%*% omega_inv %*%the_means[1:m]/m
  })
  return(F_stat)
}



# Put it all together -----------------------------------------------
generate_F_stats = function(big_T = 1000, dim = 12, lugsail_parameters = F){

  # Simulate the data 
  sim_data = matrix(rnorm(dim*big_T), nrow = big_T, ncol = dim)
  the_means = colMeans(sim_data)
  sim_data = apply(sim_data, 1, function(row) row - the_means)
  sim_data = t(sim_data)
  
  # Get autocovariance matrices
  all_autocovariances <-sapply(0:(big_T-1), R, the_sim_data = sim_data)
  all_autocovariances <- t(all_autocovariances)
  
  # What part of the autocovariance matrix is it
  rownames(all_autocovariances) = paste("Lag=", 
                                        0:(nrow(sim_data)-1), sep = "")
  colnames(all_autocovariances) = paste("m", 
                                        rep(1:(ncol(sim_data)), 
                                            each = ncol(sim_data)),
                                        rep(1:(ncol(sim_data)), 
                                            times = ncol(sim_data)), sep = "")
  
  
  # F-statistics for various b values 
  # each value corresponds to a different b 
  F_stats = sapply(try_b, get_F_stats, sim_data=sim_data, 
                   the_mean = the_means, 
                   all_autocovariances = all_autocovariances, 
                   lugsail_parameters = lugsail_parameters)
  F_stats = t(F_stats)
  colnames(F_stats) = paste("D", 1:ncol(sim_data), sep = "")
  rownames(F_stats) = paste("b=", try_b, sep="")
  
  return(F_stats)
}

# Run simulations  -----------------------------------------------
all_F_stats = replicate(100, generate_F_stats())

setwd("SimulatedFixedbCV")
t95 = apply(all_F_stats, 1:2, quantile, probs = 0.95)
write.csv(t95, "my_nw_05.cv")

t90 = apply(all_F_stats, 1:2, quantile, probs = 0.90)
write.csv(t90, "my_nw_10.cv")

t99 = apply(all_F_stats, 1:2, quantile, probs = 0.99)
write.csv(t99, "my_nw_01.cv")
setwd("..")
```

```{r}

# Need these for later
alpha_levels = 1 - .025
standard_norm_cv = qnorm(alpha_levels) 



# vec_F = c(all_F_stats)
# vec_b = rep(try_b, each =ncol(all_F_stats))
t=t95
specific_cvs = t[,1] - standard_norm_cv^2
fit = lm(specific_cvs ~ 0+  poly(try_b, 3, raw = T))

summary(fit)

```


```{r}
cv_nw_05 <- read.csv("~/Library/Mobile Documents/com~apple~CloudDocs/Desktop/UCR/Dissertation Stuff/WriteUps/cv_nw_05.csv", header=FALSE)

plot(try_b, fit$fitted.values + standard_norm_cv^2, type = "l")

# My observed values 
points(try_b, fit$model$specific_cvs + standard_norm_cv^2)

# Critical values used by LLSW 
lines(cv_nw_05$V1, cv_nw_05$V2, col = "red")

# Chisq critical value
abline(h = qchisq(.95, 1), col = "red", lty = 2)

# SPJ Closed form, second degree
SPJ2008_sq = qnorm(.975)^2 + 10.0414*try_b +16.9197*try_b^2
lines(try_b, SPJ2008_sq , col = "blue")

# legend
legend("topleft", 
       c("My fitted", "My obs", "LLSW Numeric", "Sun Analytical", "Chi Sq"), 
       col = c("black", "black", "red", "blue", "red"), 
       lty = c(1, NA, 1, 1, 2), 
       pch = c(NA, 1, NA, NA, NA))
```


```{r}
# Running average of the percentile
# Want to do a simulation large enough that they all level off

# Pick any b 
b_index = 100
m1_05_Fstats = all_F_stats[b_index, 1, ]
p = rep(NA, length(m1_05_Fstats))
for(i in 1:length(m1_05_Fstats)){
  p[i] = quantile(m1_05_Fstats[1:i], probs = 0.95)
}

plot(1:length(m1_05_Fstats), p, type = "l")
```


## Analytical Bartlett

Using SPJ2008, we can also solve for these points analytically.

Lugsail 

$$\hat{\Sigma}_L = \frac{1}{c_n} \hat{\Sigma}_b - \frac{c_n}{1-c_n} \hat{\Sigma}_{b/r}$$
Zero lugsail 

$$r = 2$$

$$c_n = r^{-q}$$

```{r}
# This is all for the bartlett kernel 

# Support function to calculation c1, c2, c3, c4
BKernel = function(x, M=1){
  w = ifelse(abs(x)<M, 1-abs(x/M), 0)
  return(w)
}
c1 = integrate(BKernel, -1, 1)$value

# the_T = 200
# b = 0.14
# M = the_T*b
# x = seq(-M, M, length.out = 100)
# y = Kernel(x)


BKernel_sq = function(x, M=1){
  w = ifelse(abs(x)<M, 1-abs(x/M), 0)
  return(w^2)
}
c2 = integrate(BKernel_sq, -1, 1)$value


BKernel_abs = function(x, M=1){
  w = ifelse(abs(x)<M, 1-abs(x/M), 0)
  return((-w*abs(x))) 
}
c3 = integrate(BKernel_abs, -1, 1)$value

BKernel_abs_sq = function(x, M=1){
  w = ifelse(abs(x)<M, 1-abs(x/M), 0)
  return((-w^2*abs(x))) 
}
c4 = integrate(BKernel_abs_sq, -1, 1)$value



# alpha: desired significance for t^2 (normal, and two sided)
get_cv_bartlett = function(b = .14, alpha= 0.05){
  
  z = qnorm(1-alpha/2)
  z_sq = z^2
  k1 = (c1 +0.5*c2)*z_sq + .5*c2*z_sq^2
  k2_1 = (.5*c1^2 + 3*c1*c2/2 + 3*c2^2/16 + c3 + .25*c4)*z_sq
  k2_2 = (-.5*c1 + 3*c1*c2/2 + 9*c2^2/16 + .25*c4)*z_sq^2+ 5*c2^2*z_sq^4/16 - (c2^2/16)*z_sq^6
  k2 = k2_1 + k2_2
  
  z_sq_b = z_sq +k1*b #+ k2*b^2
  return(z_sq_b)
} 


# Check if results fit previous plots 

```




```{r}
cv_nw_05 <- read.csv("~/Library/Mobile Documents/com~apple~CloudDocs/Desktop/UCR/Dissertation Stuff/WriteUps/cv_nw_05.csv", header=FALSE)

plot(try_b, fit$fitted.values + standard_norm_cv^2, type = "l")

# My observed values 
points(try_b, fit$model$specific_cvs + standard_norm_cv^2)

# Critical values used by LLSW 
lines(cv_nw_05$V1, cv_nw_05$V2, col = "red")

# Chisq critical value
abline(h = qchisq(.95, 1), col = "red", lty = 2)

# SPJ Closed form, second degree
SPJ2008_sq = qnorm(.975)^2 + 10.0414*try_b +16.9197*try_b^2
lines(try_b, SPJ2008_sq , col = "blue")

# SPJ Closed form, first degree (my guess)
lines(try_b, get_cv_bartlett(try_b), col ="blue", lty =2)


# legend
legend("topleft", 
       c("My fitted", "My obs", "LLSW Numeric", "SPJ (degree 2)", "SPJ Analytical (degree 1)","Chi Sq"), 
       col = c("black", "black", "red", "blue","blue" ,"red"), 
       lty = c(1, NA, 1, 1, 2, 2), 
       pch = c(NA, 1, NA, NA, NA, NA))
```

### Bartlett kernel functions 



# Lugsail 

## Simulation Lugsail 

```{r}
# Run simulations  -----------------------------------------------
lugsail_parameters = list(r = 2, c = 0.5, method = "Zero")
all_F_stats_l = replicate(500, generate_F_stats(lugsail_parameters = lugsail_parameters))

setwd("SimulatedFixedbCV")
t95_l = apply(all_F_stats_l, 1:2, quantile, probs = 0.95)
write.csv(t95_l, "my_lnw_05.cv")

t90_l = apply(all_F_stats_l, 1:2, quantile, probs = 0.90)
write.csv(t90_l, "my_lnw_10.cv")

t99_l = apply(all_F_stats_l, 1:2, quantile, probs = 0.99)
write.csv(t99_l, "my_lnw_01.cv")
setwd("..")
```


```{r}
# Running average of the percentile
# Want to do a simulation large enough that they all level off

# Pick any b 
b_index = 100
m1_05_Fstats = all_F_stats_l[b_index, 1, ]
p = rep(NA, length(m1_05_Fstats))
for(i in 1:length(m1_05_Fstats)){
  p[i] = quantile(m1_05_Fstats[1:i], probs = 0.95)
}

plot(1:length(m1_05_Fstats), p, type = "l")
```


## Analytical Lugsail 

```{r}
# This is all for the lugsail kernel 

r = 2
c = 1/r

# Support function to calculation c1, c2, c3, c4
support = function(x, M=1){
  y = (1- abs(x/M))/(1-c) - c*(1- abs(x*r/M))/(1-c)
  y
}

Kernel = function(x, M=1){
  w = ifelse(abs(x)<M, ifelse(abs(x)<M/r,  support(x), (1-abs(x/M))/(1-c)), 0)
  return(w)
}
c1 = integrate(Kernel, -1, 1)$value

# the_T = 200
# b = 0.14
# M = the_T*b
# x = seq(-M, M, length.out = 100)
# y = Kernel(x)


Kernel_sq = function(x, M=1){
  w = ifelse(abs(x)<M, ifelse(abs(x)<M/r,  support(x), (1-abs(x/M))/(1-c)), 0)
  return(w^2)
}
c2 = integrate(Kernel_sq, -1, 1)$value


Kernel_abs = function(x, M=1){
  w = ifelse(abs(x)<M, ifelse(abs(x)<M/r,  support(x), (1-abs(x/M))/(1-c)), 0)
  return((-w*abs(x))) 
}
c3 = integrate(Kernel_abs, -1, 1)$value

Kernel_abs_sq = function(x, M=1){
  w = ifelse(abs(x)<M, ifelse(abs(x)<M/r,  support(x), (1-abs(x/M))/(1-c)), 0)
  return((-w^2*abs(x))) 
}
c4 = integrate(Kernel_abs_sq, -1, 1)$value


# alpha: desired significance for t^2 (normal, and two sided)
get_cv_lugsail = function(b = .14, alpha= 0.05){
  z = qnorm(1-alpha/2)
  z_sq = z^2
  k1 = (c1 +c2/2)*z_sq + .5*c2*z_sq^2
  k2_1 = (.5*c1^2 + 3*c1*c2/2 + 3*c2^2/16 + c3 + .25*c4)*z_sq
  k2_2 = (-.5*c1 + 3*c1*c2/2 + 9*c2^2/16 + .25*c4)*z_sq^2+ 5*c2^2*z_sq^4/16 - (c2^2/16)*z_sq^6
  k2 = k2_1 + k2_2
  
  z_sq_b = z_sq +k1*b #+ k2*b^2
  return(c(z_sq_b))
}
# 
# 
# # Check if results fit previous plots 
# plot(the_bs, model_fits$fitted, type = "l", 
#      ylim = the_ylim, col = "white")
# lines(cv_nw_05$V1, cv_nw_05$V2, col = "green")
# #lines(the_bs, model_fits$SPJ2008, col = "orange")
# lines(the_bs, model_fits$SPJ2008_sq, col = "purple")
# legend("topleft", c(
#          "KS2005 fitted", 
#          "LLSW used", "Lugsail (1 degree)", "SPJ2008_sq (2 degree)"), 
#        col = c("blue", "green", "black", "purple"), 
#        lty = c(1, 1, 1, 1), 
#        pch = c( NA, NA, NA, NA))
# 
# 
# # Corresponds to Green (.95), and Purple (SPJ, .95 two sided?)
# abline(h = qchisq(.95, 1), col = "red", lty = 2)
# 
# lines(the_bs, get_cv_lugsail(the_bs))
```


```{r}

# Need these for later
alpha_levels = 1 - .025
standard_norm_cv = qnorm(alpha_levels) 



# vec_F = c(all_F_stats)
# vec_b = rep(try_b, each =ncol(all_F_stats))
t_l=t95_l
specific_cvs_l = t_l[,1] - standard_norm_cv^2
fit_l = lm(specific_cvs_l ~ 0+  poly(try_b, 3, raw = T))

summary(fit_l)
```



```{r}

cv_nw_05 <- read.csv("~/Library/Mobile Documents/com~apple~CloudDocs/Desktop/UCR/Dissertation Stuff/WriteUps/cv_nw_05.csv", header=FALSE)

plot(try_b, fit_l$fitted.values + standard_norm_cv^2, type = "l")

# My observed values 
points(try_b, fit_l$model$specific_cvs + standard_norm_cv^2)

# Critical values used by LLSW - bartlett
lines(cv_nw_05$V1, cv_nw_05$V2, col = "red")

# Chisq critical value
abline(h = qchisq(.95, 1), col = "red", lty = 3)

# SPJ Closed form, bartlett second degree
SPJ2008_sq = qnorm(.975)^2 + 10.0414*try_b +16.9197*try_b^2
lines(try_b, SPJ2008_sq , col = "blue")

# SPJ Closed form, bartlett first degree (my guess)
lines(try_b, get_cv_bartlett(try_b), col ="blue", lty =2)

# SPJ Closed form, lugsail first degree (my guess)
lines(try_b, get_cv_lugsail(try_b), lty =2)

# legend
legend("topleft", 
       c("Lugsail fitted", "Lugsail obs", "Lugsail Analytical (d1)",
         "LLSW Numeric- Bartlett", 
         "Bart (d2)", "Bart Analytical (d1)",
         "Chi Sq"), 
       col = c("black", "black", "black", 
               "red", 
               "blue","blue" ,
               "red"), 
       lty = c(1, NA, 2, 
               1, 
               2, 2, 
               3), 
       pch = c(NA, 1, NA, NA, NA, NA))
```
```{r}
plot(try_b, fit_l$fitted.values + standard_norm_cv^2, type = "l")

# My observed values 
#points(try_b, fit_l$model$specific_cvs + standard_norm_cv^2)


lines(try_b, fit$fitted.values + standard_norm_cv^2, type = "l", col = "red")

# My observed values 
#points(try_b, fit$model$specific_cvs + standard_norm_cv^2, col = "red")
```

